---
title: "Simple Linear Regression"
output: 
  html_document:
    theme: simplex
    code_folding: hide
---

```{r, message=FALSE, warning=FALSE}
# Load your libraries
library(car)
library(tidyverse)
library(pander)
NBA <- read.csv("../../Data/NFL.csv", header=TRUE)

# Load your data after saving a csv file in your Data folder.
# You can use either 
#   someName <- read.csv("../Data/YourDataFileName.csv", header=TRUE)
# or
#   library(readr)
#   someName <- read_csv("../Data/YourDataFileName.csv")

# Don't forget to run "Session -> Set Working Directory -> To Source file location"

```


```{r}

```


## Analysis
<!-- Directions

Come up with a simple linear regression of your own creation. 

* Write the Background and clearly state your question. Then collect data and perform the linear regression analysis in order to answer your question. Use the proper order of first, ask the question, then second, figure out the answer.

* You should collect both the quantitative response variable and the quantitative explanatory variable yourself. This can be data you collect from
    - the internet (like weather data, Facebook data, or sports data) 
    - your own experiment 
    - your own observational study
* However,     
    - The data should not be a single pre-existing dataset. It must be something that you piece together yourself.

* You need at least $n=3$ $(X,Y)$ pairs to perform the regression. However, your regression will only be useful if you can get around $n=10$ or more observations.

-->


## Background

For this project I've decided to look at NBA teams and see how their 2018-19 regular season win amounts predict their post season win amounts. Since only 16 teams make the playoffs each year, I will only have 16 data points. I will predict this using a simple linear regression model. 

## Analysis
In this analysis, regular season wins will be my explanatory variable while post-season wins will be my response variable. Since I am trying to estimate this relationship using a linear model, I will be analyzing the slope of this regression line. If the slope is zero, then there is no significant relationship between regular season wins and post-season wins. Alternatively, if the slope is significantly different than 0, then there *is* a significant relationship. 

$$
H_0 : \beta = 0 \\
H_a : \beta \neq 0 \\
\alpha = 0.05
$$
```{r}
plot(PSW ~ RSW, data = NBA, xlab = "Regular Season Wins", ylab = "Post-Season Wins", main = "2018-19 NBA Win Totals", pch = 21, bg = "blue")
NBA.lm <- lm(PSW ~ RSW, data = NBA)
abline(NBA.lm, col = "blue")
```

A scatterplot of the points would indicate that there is indeed a positive trend between the two variables, but we will run a linear regression test to make sure.

$$
\hat Y_i = \beta_0 + \beta_1X_i
$$

In this estimated regression line, $\beta_0$ is the Y-intercept and $\beta_1$ is the slope. 
```{r}
pander(summary(NBA.lm))
```
After running our linear model we see that both of the P-values for our slope and Y-intercept are lower than our $\alpha$ of 0.05, meaning that we can reject the null hypothesis that our $\beta = 0$. 

Our updated regression line, which is superimposed over the scatterplot, would look like this: 

$$
\hat Y_i = -32.81 + 0.7559
$$

## Interpretation
Since we were able to reject our null hypothesis, we do know that amount of regular season wins *does*, to an extent, predict amount of post season wins. For every regular season win a team has, they can expect to have about 0.76 more post season wins. While our regression line is required to have a slope (in this case -32.81), this particular coefficient doesn't serve any other purpose than illustrating the best-fit line. For example, since none of these playoff teams had 0 regular season wins, we don't need to know how many playoff wins a 0 regular season win team would have.

But before we fully conclude that our regression model is correct, we must run diagnostic plots for this data set to make sure our requirements for linear regression are met.

```{r}
par(mfrow = c(1,3))
plot(NBA.lm, which = 1:2)
plot(NBA.lm$residuals, main = "Residuals vs. Order", xlab = "", ylab = "Residuals")
```
According to these three plots, all five of our asssumptions have been met: 

1. The true regression relation between $Y$ and $X$ is linear

2. Our error terms are normally distributed

3. They have constant variance between them 

4. They error appear to be independent from one another

5. The fixed $X_i$ values are fixed 

We can now safely assume that the results from our linear regression model are reliable and correct. 